TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-20 paper/paper.tex
Conclusion

\section{Conclusion}\label{sec:conclusion}
To do: Mention items:
\begin{enumerate}
	\item{With current TCP congestion control algorithms behaving fair: No traffic control is currently needed & there is no impact on service and availability for customers}
	\item{BBR is best performing algorithm of five tested}
	\item{DCTCP is only suitable when both server and client are in same datacenter}
	\item{Windows needs further testing}
\end{enumerate}

>>>>

\section{Conclusion}\label{sec:conclusion}
Our main research question is: {\it How can a datacenter provide a reliable and performant environment for customers when multiple TCP congestion control algorithms are used in the network?}

The results have shown that the current default TCP congestion control algorithms are showing a fair behavior: The bandwidth is allocated equally among all nodes. Therefore, currently no traffic control is needed, unless someone would create an unfair TCP congestion control algorithm. This can be detected by one of the monitoring solutions proposed in this paper.

To do: Mention items:
\begin{enumerate}
	\item{With current TCP congestion control algorithms behaving fair: No traffic control is currently needed & there is no impact on service and availability for customers}
	\item{BBR is best performing algorithm of five tested}
	\item{DCTCP is only suitable when both server and client are in same datacenter}
	\item{Windows needs further testing}
\end{enumerate}
